### 2021-03-16 papers/SYRCoSE/intro.tex
SYRCoSE: reworking the introduction

>>>>

Event structures is a mathematical formalism introduced 
by Winskel~\cite{Winskel:86} as a semantic domain of concurrent programs.
In recent years there is a renewed interest in event structures, 
with the applications of the theory ranging from relaxed memory models%
~\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19}
to model-based mutation testing~\cite{Fellner-al:VMCAI2020}.
\eupp{perhaps, we could add more citations once the related work is ready.}

The main advantage of the event structures 
compared to traditional interleaving semantics 
is that they give a more compact and consice 
representation of progams' behavior.
For example, consider the following code snippet.

\input{fig/intro-prog.tex}

Under the interleaving semantics 
it has $3! = 6$ traces with each trace consisting of $4$ events,
as depicted on \cref{fig:intro-traces}.
Event themselves represent atomic side-effects 
of instructions' execution. In our case 
it is either a write of a value to a shared variable $\wlab{x}{a}$,
or a read of a particular value from a shared variable $\rlab{x}{a}$.

\input{fig/intro-traces.tex}

The same information can be encoded in a single 
event structure containing $6$ events in total
(see \cref{fig:intro-es}). 
In the event structure there are two types of edges 
between the events. The gray arrows $e_1 \arrowCA e_2$ 
represent the \emph{causality relation}, a 
partial order reflecting the causal relationship
between the atomic events of computation.
The red edges $e_1 \arrowCF e_2$ represent 
the \emph{conflict relation} which is 
a symmetric and irreflexive relation 
encoding mutually exclusive events.
Each particular trace can be extracted from the event structure
as a linearisation of some \emph{configuration}, 
that is a causally-closed and conflict-free 
subset of events.

\input{fig/intro-es.tex}

\eupp{Continue from here...}
